Feature Selection and Classification of \\ Spam on Social Networking Sites

### 2012-05-09 docs/paper/paper.tex
update

\begin{itemize}
\item \textbf{Advance Fee Fraud} We observed this scam to come in various flavors.  (inheritance, lottery,  etc)
\item \textbf{Romance Scams:} These 
\item \textbf{Sexual Solicitation}
\item \textbf{Porn Ads}
\item \textbf{Advertising External Sites}
\item \textbf{Webcam Ads}
\item \textbf{Money Muling}
\item \textbf{Begging \& Gift Requests}
\item \textbf{Business Proposals}
\end{itemize}

@@

%classification:
%- implemented 3 models: naive bayes, linear regression, and SVM.
%- used scalanlp for naive bayes
%- used matlab for linear regression with ridge regularization.
%- also attempted logistics regression with scalanlp, but training result was buggy (always output 0 probably. perhaps a bug in scalanlp)
%
%- naive bayes is super fast. accuracy around 80%. when expert features are added, accuracy dropped.
%
%- SVM is slow, and doesn’t produce very good result. Suspect we don’t have enough training data (22k training examples, 5k features)
%
%- linear regression performed the best, with an AUC of 0.xx. When expert features are added, AUC went up to 0.xx.
%

@@

All of our linear regression code was implemented in MATLAB because of its ease-of-use 
and optimizations on matrix multiplications. We read in the text-based feature dictionaries and feature matrix
representations created above,

%We parse the messages from the text format produced by our cleaning script, using the dictionary generated earlier map words to integers, saving the feature data into two sparse matrices. The first matrix only includes the bag-of-words representation of the message body, while the second includes the expert features as well.  Matlab uses Compressed Sparse Column format, so we actually stored the matrix $X'$ because the dictionary is very sparse.

%For each feature set, the actual matrix multiplications were done using the sparse $X$ matrix along with our $y$ vector and the ridge parameter. The multiplication $X'X$ takes up too much memory if we use the entire dictionary, so we chose to limit the dictionary size. We found that a dictionary of the 10,000 most frequent words gave sufficient features while also being computable using MATLAB's built-in sparse matrix multiplications. We also tried using a dictionary of 15,000 words, but only had a marginal improvement along with much slower execution. Using our 10,000 word dictionary, we calculated the performance of our matrix multiply to be 0.123 Gflops/s by dividing the number of non-zero elements in our matrices by the time to compute the multiplication. 
%
%
%Since we used ridge regression, we had the ability to tune the $\lambda$ parameter in order to get the best performance. As shown in figure \ref{fig:lambda}, we observed an AUC improvement of about .5\% between the default value of 1 and a tuned parameter of 1500. This is a fairly major difference since the AUC is at 93\% using the default value. Additionally, we also noticed a major difference in the top words when using better $\lambda$ values. Using the default value of 1, our top words included obscure words including ``\_c'', ``\_j'', ``donovan'', and ``matlock.'' When we used the tuned $\lambda$ value of 1500, the words were much more representative, as shown in table \ref{tab:words}.
%

@@

We tried a number of values for $\lambda$: 1, 10, 50, 100, 500, 1000, 1500, 3000. Figure \ref{fig:lambda}
\ref{fig:roclin}

@@

@@

% LR + expert
\begin{table}
\begin{tabular}{l|r||l|r}
\multicolumn{2}{c}{\textbf{Ham}} & 
\multicolumn{2}{c}{\textbf{Spam}} \\
\hline
\textbf{Feature} & \textbf{Weight} & \textbf{Feature} & \textbf{Weight} \\
\hline

requests & -0.1349 & F-country\_match & 0.3365\\
giggle & -0.1257 & sex & 0.1954\\
turkey & -0.1213 & cafe4tune & 0.1723\\
hw & -0.1148 & register & 0.1324\\
F-photo\_exists & -0.1087 & F-spam\_country & 0.1231\\
xxx & -0.1047 & rochelle & 0.1054\\
goin & -0.1008 & m? & 0.1019\\
teacher & -0.1006 & tony & 0.1017\\
happy & -0.0912 & hehe & 0.0991\\
yie & -0.0904 & oky & 0.0968\\
tea & -0.089 & sexy & 0.0967\\
snail & -0.0852 & ewelina & 0.0874\\
malaysia & -0.084 & card & 0.0866\\
russian & -0.0832 & return & 0.0856\\
fall & -0.0805 & video & 0.0842\\
question & -0.0789 & pay & 0.0841\\
ann? & -0.0785 & nas? & 0.0839\\
learn & -0.0784 & model & 0.0826\\
new & -0.0783 & displaying & 0.0808\\
daichi & -0.0775 & k?  & 0.0806\\

\end{tabular}
\caption{Linear Regression top features (bag-of-words \& expert features) with weights. Expert features
are denoted by an 'F-' prefix.}
\label{tab:lrfeats}
\end{table}

>>>>

\begin{itemize}
\item \textbf{Advance Fee Fraud} 
\item \textbf{Romance Scams} 
\item \textbf{Sexual Solicitation}
\item \textbf{Porn Ads}
\item \textbf{Advertising External Sites}
\item \textbf{Webcam Ads}
\item \textbf{Money Muling}
\item \textbf{Begging \& Gift Requests}
\item \textbf{Business Proposals}
\end{itemize}

@@

%classification:
%- implemented 3 models: naive bayes, linear regression, and SVM.
%- used scalanlp for naive bayes
%- used matlab for linear regression with ridge regularization.

@@

All of our linear regression code was implemented in MATLAB because of its ease-of-use 
and optimizations on matrix multiplications. We read in the text-based feature dictionaries and the feature matrix
representations created above, which is stored as a sparse matrix (efficiently represented in Matlab as 
in Cmmpressed Sparse Column format).

We used ridge regression, which gave us the opportunity to tune a $\lambda$ parameter in order to 
regularize the vector components for better performance.

@@

We performed 10-fold cross-validation with $\lambda=50$, which resulted in a mean AUC of 0.886 and mean lift of 
29.216 for the bag-of-words LR model. After adding the expert features, the mean AUC climbed to 0.951 with a mean 
lift of 41.584. Figure \ref{fig:roclin} show ROC curves for 1-fold cross-validation on both of these models.

As shown in figure \ref{fig:lambda}, we tested a number of values for $\lambda$, the ridge regression parameter. 
Since the AUCs corresponding to $\lambda$ for both models appear to peak between 30 and 50, we may have been able to 
get a slightly higher AUC by using a lower $\lambda$.

@@

Tables \ref{tab:lrfeats} and \ref{tab:lrfeatse} list the top-weighted terms for the bag-of-words and expert feature 
models. The spam-related words appear in line with our expectations, with sex-related terms prevalent, as well as
words that might indicate advertisements (``cafe4tune," for example, appears to be a competing SNS). Table \ref{lrfeatse} 
shows that IP-profile country mismatch and membership of the IP-detected country in our ``high-risk" list were 
strong predictors that a message might be spam. Likewise, whether or not a user had photos was a righ-ranking indicator 
of ham.

@@

% LR + expert
\begin{table}
\begin{tabular}{l|r||l|r}
\multicolumn{2}{c}{\textbf{Ham}} & 
\multicolumn{2}{c}{\textbf{Spam}} \\
\hline
\textbf{Feature} & \textbf{Weight} & \textbf{Feature} & \textbf{Weight} \\
\hline
requests & -0.1349 & F-country\_match & 0.3365\\
giggle & -0.1257 & sex & 0.1954\\
turkey & -0.1213 & cafe4tune & 0.1723\\
hw & -0.1148 & register & 0.1324\\
F-photo\_exists & -0.1087 & F-spam\_country & 0.1231\\
xxx & -0.1047 & rochelle & 0.1054\\
goin & -0.1008 & m? & 0.1019\\
teacher & -0.1006 & tony & 0.1017\\
happy & -0.0912 & hehe & 0.0991\\
yie & -0.0904 & oky & 0.0968\\
tea & -0.089 & sexy & 0.0967\\
snail & -0.0852 & ewelina & 0.0874\\
malaysia & -0.084 & card & 0.0866\\
russian & -0.0832 & return & 0.0856\\
fall & -0.0805 & video & 0.0842\\
question & -0.0789 & pay & 0.0841\\
ann? & -0.0785 & nas? & 0.0839\\
learn & -0.0784 & model & 0.0826\\
new & -0.0783 & displaying & 0.0808\\
daichi & -0.0775 & k?  & 0.0806\\
\end{tabular}
\caption{Linear Regression top features (bag-of-words \& expert features) with weights. Expert features
are denoted by an `F-' prefix.}
\label{tab:lrfeatse}
\end{table}
